---
title: Data Analysis Report
subtitle: Uncovering spatial and verbal cognitive profiles in aphantasia through unsupervised clustering
# setting for proper numbering of sections
crossref: 
  chapters: true
  custom:
    - kind: float
      key: suppfig
      reference-prefix: Figure S
      space-before-numbering: false
    - kind: float
      key: supptbl
      reference-prefix: Table S
      space-before-numbering: false
supptbl-cap-location: top
echo: false # do not show the code unless explicitly asked
params:
  save_figures: false
format: html
---

:::: {.callout-note collapse="true"}
# Packages and pipeline

```{r}
#| label: setup
#| echo: true
#| code-fold: false

if (!requireNamespace("pacman")) install.packages("pacman")
pacman::p_load(
  conflicted, 
  here,
  fs, 
  ggplot2,
  mclust,
  NbClust,
  patchwork,
  purrr,
  sessioninfo
)

# source all our custom functions
dir_ls(here("R"), type = "file", recurse = TRUE) |> walk(source)

# resolve package conflicts
conflicts_prefer(
  dplyr::filter(), 
  dplyr::select(),
  scales::rescale(), 
  purrr::map(),
  .quiet = TRUE
  )
```

Most of the steps of the data analysis were performed using functions defined in 
external R scripts in the `R/` directory (loaded in the chunk above). 
The interested reader can find their code in the tab below. 

:::{.callout-note collapse="true"}
## Custom functions

First, the `import_jatos_data` is a long function that extracts the data from the
raw JATOS files, tidies it, computes various scores, exports data for manual scoring
or loads the manually scored data, exports the data to Excel, CSV and RDS formats,
and returns a list with the data and metadata. This way, the data used is always
recreated from the raw data, enhancing reproducibility.

```{r}
#| label: add-import
#| add-from: ../R/01_import/import-jatos-data.R
#| code-summary: Data import function
#| echo: true

#
```

Four functions were created to manipulate the data in various ways.

```{r}
#| label: add-scale-vars
#| add-from: ../R/02_wrangle/scale-vars.R
#| code-summary: Scale variables from their original range to 0-1
#| echo: true

#
```

```{r}
#| label: add-scale-reduce-vars
#| add-from: ../R/02_wrangle/scale-reduce-vars.R
#| code-summary: "Scale variables and compute reduced variables (based on correlations)"
#| echo: true

#
```

```{r}
#| label: add-merge
#| add-from: ../R/02_wrangle/merge-clusters.R
#| code-summary: Add the clusters computed to the main dataframe
#| echo: true

#
```

```{r}
#| label: add-longer
#| add-from: ../R/02_wrangle/get-longer.R
#| code-summary: Pivot the table to a long format and use pretty names
#| echo: true

#
```

Three functions were dedicated to modelling tasks.

```{r}
#| label: add-correlate
#| add-from: ../R/03_model/correlate-vars.R
#| code-summary: Compute correlations or partial correlation on the original variables
#| echo: true

#
```

```{r}
#| label: add-model-groups
#| add-from: ../R/03_model/model-groups.R
#| code-summary: "Model all the variables with the Group, Cluster or Subcluster (+ Age) as predictors"
#| echo: true

#
```

```{r}
#| label: add-model-lives
#| add-from: ../R/03_model/model-lives.R
#| code-summary: Assess association of education, field of study and occupation with Group, etc.
#| echo: true

#
```

Finally, four functions were created to plot the data, a helper function was used
to save figures in appropriate formats conveniently, and a function helped 
generating $\LaTeX$ tables automatically for the manuscript.

```{r}
#| label: add-violins
#| add-from: ../R/04_plot/plot-violins.R
#| code-summary: Plot group scores as violin-dot figures
#| echo: true

#
```

```{r}
#| label: add-radars
#| add-from: ../R/04_plot/plot-radars.R
#| code-summary: Plot group, cluster or subcluster scores as radars
#| echo: true

#
```

```{r}
#| label: add-correlation-plots
#| add-from: ../R/04_plot/plot-correlations.R
#| code-summary: Plot correlation matrices and graphs
#| echo: true

#
```

```{r}
#| label: add-bic
#| add-from: ../R/04_plot/plot-clusters-bic.R
#| code-summary: Plot BIC evaluation of GMMs for clustering
#| echo: true

#
```

```{r}
#| label: add-save
#| add-from: ../R/04_plot/save-plots.R
#| code-summary: Save plots in appropriate formats
#| echo: true

#
```

```{r}
#| label: add-latex
#| add-from: ../R/04_plot/get-latex-table.R
#| code-summary: "Print $\\LaTeX$ tables for the manuscript"
#| echo: true

#
```
:::

The pipeline code below then runs all of these functions sequentially, 
sometimes saving heavy computations along the way. It saves the figures if this
notebooks was parametrised to do so with `params: save_figures: true`.
This pipeline is designed to be fully reproducible by anyone using the `renv` 
R environment from the project that has the raw JATOS data stored in the 
`data/raw-data/` directory.

```{r}
#| label: pipeline
#| echo: true
#| code-summary: Data analysis pipeline

# load the data directly from the raw files
df <- import_jatos_data()$data_final

# compute simple and partial correlations
corrs_simple  <- correlate_vars(df, partial = FALSE, correction = "bonferroni")
corrs_partial <- correlate_vars(df, partial = TRUE,  correction = "bonferroni")

# variables selected for clustering after the analysis of partial correlations
selected_vars <- c(
  "visual_imagery", "sensory_imagery", 
  "spatial_imagery", "verbal_strategies",
  "fluid_intelligence", "verbal_reasoning", 
  "span_spatial"
)

# determine the best model (GMM) and number of clusters for clustering with BIC
bic <- df |> scale_reduce_vars() |> select(any_of(selected_vars)) |> mclustBIC()

# compute the clustering on the selected variables with the model
clustering <- 
  df |> 
  scale_reduce_vars() |> 
  select(any_of(selected_vars)) |>
  Mclust(verbose = FALSE)

# add the clusters and the reduced variables to the main dataset
df2 <- merge_clusters(df_raw = df, df_red = scale_reduce_vars(df), clustering)

# create a long format of this final dataset for modelling and plotting
df_long <- df2 |> scale_vars() |> get_longer()

# model all the variables with the groups, clusters and subclusters and save
# them, or simply load them if they exist in the files 
models_path <- here("data/r-data-structures/models.rds")

if (!file_exists(models_path)) {
  group_models      <- df2 |> get_longer() |> model_groups(groups = Group)
  cluster_models    <- df_long |> model_groups(groups = Cluster)
  subcluster_models <- df_long |> model_groups(groups = Subcluster)
  
  models <- list(
    group_models      = group_models,
    cluster_models    = cluster_models,
    subcluster_models = subcluster_models
  )
  
  saveRDS(models, models_path)
  
  } else models <- readRDS(models_path)

# model the education, field of study and occupation with groups, etc.
lives <- list(
  group      = model_lives(df2, group),
  cluster    = model_lives(df2, cluster),
  subcluster = model_lives(df2, subcluster)
)

# Produce the plots for all these outputs --------------------------------------

# the group comparisons, as violins
p_groups_violins <- plot_violins(df_long, var_selection = "original")
# and as radars
p_groups_radar   <- plot_radars(df_long, Group,  var_selection = "original")

# correlation matrices and graphs
p_partial <- plot_correlations(corrs_partial)
p_simple  <- plot_correlations(corrs_simple)

# BIC values for all models and number of clusters tested
p_bic <- plot_clusters_bic(clustering)

# radars of the cluster and subcluster scores
p_clusters <- 
  plot_radars(df_long, Cluster, r_off = 6) + 
  plot_radars(df_long, Subcluster, l_off = 6)

# save the figures if this notebook is parametrised to do so
if (params$save_figures) {
  ggsave_double_col("figures/groups-violins.pdf", p_groups_violins, height = 88)
  ggsave_single_col("figures/groups-radar.pdf",   p_groups_radar,   height = 88)
  
  ggsave_double_col("figures/correlations-partial.pdf", p_partial, height = 120)
  ggsave_double_col("figures/correlations-simple.pdf",  p_simple,  height = 120)
  
  ggsave_single_col("figures/clusters-bic.pdf",    p_bic,      height = 88)
  ggsave_double_col("figures/clusters-radars.pdf", p_clusters, height = 90)
}
```
::::

This document contains all the data analysis process related to the article in the subtitle.
This analysis should be fully reproducible. See the tab below for the details on how to do so.

&nbsp;
&nbsp;
&nbsp;

::: {.callout-note collapse="true"}
# Session information

```{r}
#| label: session-information

sessioninfo::session_info(pkgs = "attached")
```
:::